\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-06-24 lang-design.tex
Rephrase Wording.

First and foremost, we don't want to throw away some basic good
properties of Coq. \textlabel{Req~(0A)}{langdesign-req0}~\textbf{we
want to retain incremental (modular) type checking}. Notice that, the
modularity here in Coq is a bit different from other languages, because
Coq supports \textit{interactive} theorem proving, so we actually need
\textit{statement-wise} incremental type checking, not only for avoiding
re\-compilation, but also to enable immediate feedback and incremental
type-checking for the Coq developer. We don't want our family to ruin
this conventional routine of interactive development.
\textlabel{Req~(0B)}{langdesign-req0b}~\textbf{we also want to keep the
computational property of Coq when using families}. Coq, as a constructive
logic, has been famous for its ability to do calculations and extract
programs. We don't want our Family facility to ruin this: the developers
should be able to project field as first-class value just like Coq's
Module.

>>>>

First and foremost, we don't want to throw away some basic good
properties of Coq. \textlabel{Req~(0A)}{langdesign-req0}~\textbf{we
want to retain incremental (modular) type checking}. Notice that, the
modularity here in Coq is a bit different from other languages, because
Coq supports \textit{interactive} theorem proving, so we actually need
\textit{statement-wise} incremental type checking, not only for avoiding
re\-compilation, but also to enable immediate feedback and incremental
type-checking for the Coq developer. We don't want our family to ruin
this conventional routine of interactive development.
\textlabel{Req~(0B)}{langdesign-req0b}~\textbf{we also want to keep the
computational ability of Coq when using families}. Coq, based on constructive
logic, can consider proof as programs. 
We don't want our Family facility to ruin this when incorporated with 
the remaining parts of Coq: 
the developers should be able to project fields of families 
as first-class value just like how they can project fields of Coq's Module.
